Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spanning 500\,Parsecs

### 2021-03-18 cluster_paper/ms.tex
made li plot better

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
			\includegraphics[width=1\textwidth]{f5a.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Lithium in the core and halo of NGC\,2516.}
  Equivalent width of the 6708\,\AA\ doublet is shown
  versus extinction-corrected color for all kinematic \cn\ members
  with Gaia-ESO ($N=452$) or GALAH ($N=107$) spectra available.
  The GALAH spectra comprise slightly over half of the halo stars,
  due to the non-targeted selection function of that survey.
  The gray points are Keck-HIRES measurements of stars with detected
  transiting planets from the Kepler mission
  \citep{berger_identifying_2018}.
  Points with ${\rm EW}\approx0\,$m\AA\ are non-detections.
  \label{fig:lithiumcorehalo}
  }
\end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
		\includegraphics[width=1\textwidth]{f5b.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Lithium and rotation in NGC\,2516.}
		Points show all kinematic \cn\ members with TESS rotation
		periods in the Gaia-ESO or GALAH surveys, and are colored by
		equivalent width.
	   Non-detections appear with ${\rm EW}\approx0\,$m\AA.
	The K-dwarfs shows a similar lithium-rotation correlation
		to what has been previously observed,
		and is discussed in Section~\ref{subsec:lithium}.
		\label{fig:lithiumrot}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
			\includegraphics[width=1\textwidth]{f5a.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Lithium in the core and halo of NGC\,2516.}
  Equivalent width of the 6708\,\AA\ doublet is shown
  versus extinction-corrected color for all kinematic \cn\ members
  with Gaia-ESO ($N=452$) or GALAH ($N=107$) spectra available.
  The GALAH spectra comprise slightly over half of the halo stars,
  due to the non-targeted selection function of that survey.
  The gray points are Keck-HIRES measurements of stars with detected
  transiting planets from the Kepler mission
  \citep{berger_identifying_2018}.
  Points with ${\rm EW}\approx0\,$m\AA\ are non-detections.
  \label{fig:lithiumcorehalo}
  }
\end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
		\includegraphics[width=1\textwidth]{f5b.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Lithium and rotation in NGC\,2516.}
		Points show all kinematic \cn\ members with TESS rotation
		periods in the Gaia-ESO or GALAH surveys, and are colored by
		equivalent width.
    Points with reported equivalent widths below 20\,m\AA\ (including
    non-detections) are shown with gray crosses.
    The lithium-rotation correlation for the K-dwarfs
    has been observed in other young clusters, and is discussed in
    Section~\ref{subsec:lithium}.
		\label{fig:lithiumrot}
	}
\end{figure*}
